Distributed Multi-Heuristic A* (HAMSTAR)

### 2014-12-11 paper.tex
broadcast section

We considered two communication models for our algorithm. The first one, which we call the one-on-one model, has the anchor periodically send all children a table of states. The table contains information for new states that were either received by the anchor, or calculated by the anchor, since the last time the anchor communicated with this child. Each child frequently checks for incoming messages using the \emph{MPI\_Iprobe} command; if a message is detected, the child receives the incoming data using \emph{MPI\_Recv} and responds with its own table of states. The anchor sends messages to each child one at a time, moving on to the next child when a response is received. Once the data has been sent to all children, the anchor will run its own iterations until the next cycle should begin.

The second communication model involves a periodic broadcast using the \emph{MPI\_Bcast} command. After a pre-determined number of iterations, all child machines send their new states to the anchor using \emph{MPI\_Gather}. The anchor sifts through these responses, and keeps only the best $g$-value for each state. Every state that has had a new best $g$-value found is then broadcast to all the child machines.

The one-on-one communication model has the benefit that it does not require all machines to cease work while communication happens; only the anchor and a single child machine need to participate in the communication. The downside is that the anchor must then do $O(N)$ communications, where $N$ is the number of children, and the time it takes to propogate the new state tables across the entire system is also $O(N)$. Broadcasts, on the other hand, require a simultaneous call from all machines. This generally requires more overhead, because it is unlikely that all machines will call the command at precisely the same time. However, once called, the Broadcast command allows the anchor to only send the data to a few machines in the network. These machines, in turn, forward the data to other machines, and so on. Thus, the anchor does not spend any more time communicating than any other machine in the system, and the new state table is propagated in $O(\log(N))$ time.

We ultimately chose the broadcast model for our implementation due to the more balanced workload on the anchor. In fact, in the specific problem we analyzed (the sliding tile puzzle), using the one-on-one communication model was not a viable option; it would take longer for the anchor to process incoming states and send them out than it would for child nodes to expand new states.

>>>>

We considered two communication models for our algorithm. The first, which we call the one-on-one model, has the anchor periodically send all children a table of states. The table contains information for new states that were either received or calculated by the anchor since its most recent communication with this child. Each child frequently checks for incoming messages using the \emph{MPI\_Iprobe} command: if a message is detected, the child receives the incoming data using \emph{MPI\_Recv} and responds with its own table of states. The anchor sends messages to each child one at a time, moving on to the next child when a response is received. Once the data has been sent to all children, the anchor will run its own expansion iterations until a time when the next cycle should begin.

The second communication model involves a periodic broadcast using the \emph{MPI\_Bcast} command. After a pre-determined number of iterations, all child machines send their new or updated states to the anchor using \emph{MPI\_Gather}. The anchor sifts through these responses, and keeps only the best $g$-value for each state. Every state that has had a new best $g$-value found is then broadcast to all the child machines.

The one-on-one communication model has the benefit that it does not require all machines to cease work while communication happens; only the anchor and a single child machine need to participate in the communication. The downside is that the anchor must then do $O(N)$ communications, where $N$ is the number of children, and the time it takes to propogate the new state tables across the entire system is also $O(N)$. Broadcasts, on the other hand, require a simultaneous call from all machines. This generally requires more overhead, because it is unlikely that all machines will call the command at precisely the same time. However, once called, the Broadcast command allows the anchor to only send the data to a few machines in the network. These machines, in turn, forward the data to other machines, and so on. Thus, the anchor does not spend significantly more time communicating than other machines in the system, and the new state table is propagated in $O(\log(N))$ time.

We ultimately chose the broadcast model for our implementation due to the more balanced workload on the anchor. In fact, for the case of the sliding tile puzzle, the one-on-one communication model was not a viable option; it would take longer for the anchor to process incoming states and send them out than it would for child machines to expand new states.
